---
title: "20181003a Phenotypes"
author: "cheungngo"
date: "October 3, 2018"
output: word_document
---

###

## Package and data

```{r COPD data, eval=FALSE}
library(BiocInstaller)
biocLite('COPDSexualDimorphism.data')
```

```{r loading the library, message=FALSE}
library(COPDSexualDimorphism.data)
data(lgrc.expr.meta)
# The variable pkyrs in the expr.meta data.frame represents pack years smoked
# Other variables include gender (self-explanatory) and diagmaj (disease status)
```

```{r names of dataframe}
names(expr.meta)
```


###

## What is the number of female participants in this study?:

```{r}
unique(expr.meta$gender)
```

```{r}
sum(expr.meta$gender=='2-Female')
```

###

## What is the median of the distribution of pack years smoked in this cohort (women and men)?

```{r}
median(expr.meta$pkyrs)
```

###

## True or False: The distribution of pack-years smoked is well-approximated by a Gaussian (Normal) probability distribution.

```{r}
qqnorm(expr.meta$pkyrs)
# FALSE
```

###

## Which of the following is an aspect of the display that would suggest caution in using the t test in comparing males and females with respect to pack years smoked?

```{r}
boxplot(pkyrs~gender, data=expr.meta)
# plot 01
# Distributions appear quite asymmetric, with long tails skewed towards high values.
```

###

## Variable transformation using boxcox

```{r}
# transform the pkyrs into a positive var for analysis
expr.meta$pyp1 = expr.meta$pkyrs+1
```

```{r, message=FALSE}
library(MASS)
```

```{r}
lm1 = lm(pyp1~gender, data=expr.meta)
bc1 = boxcox(lm1)
lambda = bc1$x[which(rank(-bc1$y)==1)]
lambda
# if lambda is 0.5, we use sqrt(pyp1)
```

```{r}
boxplot(I(pyp1^lambda)~gender, data=expr.meta)
# plot 02
# the skewness seems disappeared
```
