---
title: "20181002b Gene signature assessment"
author: "cheungngo"
date: "2 October 2018"
output: word_document
---


###


## Gene signature assessment


### The 70-gene diagnostic signature for breast cancer progression risk

###

```{r the genefu package, eval=FALSE}
library(BiocInstaller) 
biocLite("genefu")
#  "R package providing various functions relevant for gene expression analysis with emphasis on breast cancer"
```

###

```{r 70 gene signature, message=FALSE}
library(genefu) 
data(sig.gene70) 
dim(sig.gene70) 
head(sig.gene70)[,1:6]
```

###

### How many components of the signature have a missing value for the associated NCBI gene symbol?

###

```{r}
sum(is.na(sig.gene70$NCBI.gene.symbol))
```

### Kinases in the 70 gene signature

#### You can use grep on the Description field of the sig.gene70 data.frame to search for substrings of long gene names
#### How many of the members of the 70-gene signature are genes coding for kinases?

###

```{r grep the kinase}
length(grep('kinase',sig.gene70$Description))
```

###

### Some exploration in the genefu

###

```{r data in genefu,eval=FALSE}
data(package = 'genefu')
```

```{r columns in genefu}
names(sig.gene70)
```